Manuscript title here

### 2021-08-25 sub-projects/trawl/docs/ms/ms.RMD

---
title: "Manuscript title here"
author: 
- name: James R Junker
  affiliation: Louisiana Universities Marine Consortium
output:
   word_document:
     reference_docx: docx_template.docx
   pdf_document:
     keep_tex: true
   html_document: default
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \linenumbers
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---
```{r Rmarkdown setup, include = FALSE, echo=F, warning=FALSE, message=FALSE}

source(here::here("datascript.R"))
source(here::here("analyses/trawl/R/Lorenz.R"))
source(here::here("analyses/trawl/R/Evenness.R"))

TB_trawl_data = TB_trawl_data %>%
   dplyr::filter(year %ni% c("2020","2021"))

@@

Species names were checked for typos and confirmed using the *gni_parse* function from the *taxize* package [@chamberlain2020] and further standardized to consistent taxonomic resolution for entire data series (Supplemental materials). We measured multiple aspects of species richness, first to track the uncorrected accumulation of species over time we filtered species from the data set after first occurrence. We then aggregated all trawls within a calendar year and calculated two measures of species richness, accounting for differences in sampling effort among years. The first measure was asymptotic species richness, *S~asymp~*, using the Chao1 estimator [@chao1984][@chao1987]. This metric is highly correlated with measured richness, *S* [@mcgill2011], but attempts to extrapolate the total species richness based on incomplete sampling. Second, we attempted to account for differences in effort among years by estimating the effort-controlled rarefied species richness, *S~n~*, which provides the expected number of species given a defined number of *n* individuals sampled [@gotelli2001]. *S~n~* estimates for yearly aggregated data, *n* was calculated by the minimum number of trawls within a year multiplied by `r n_year`. We calculated *S~asymp~* and *S~n~* using the mobr package [@mcglinn2019][@mcglinn2021a].

@@

TB_trawl_sampling = TB_trawl_data %>%
  # exclude 2020 & 2021
  dplyr::filter(year %ni% c("2020","2021")) %>%
   dplyr::select(Date, year, Common_name, Abundance) %>%
   group_by(year) %>%
   dplyr::summarise(trawl_days = length(unique(Date)),
                    S = length(unique(Common_name)),
                    individuals = sum(Abundance, na.rm = TRUE))

TB_trawl_taxasite <- TB_trawl_data %>%
  # exclude 2020 & 2021
  dplyr::filter(year %ni% c("2020","2021")) %>%
  dplyr::select(Date, Common_name, Abundance) %>%
  group_by(Date, Common_name) %>%
  summarise(Abundance = sum(Abundance)) %>%
  na.omit %>% group_by(Date) %>%
  # remove trawls with less than 20 individuals 
  # dplyr::filter(sum(Abundance) >=20) %>%
  group_by(Date, Common_name) %>%
  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
  ungroup() %>%
  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
                biweekly = ceiling(julian_date/30),
                month = month(Date),
                year = year(Date)) %>%
  dplyr::select(julian_date, Date, year, month, biweekly, everything())

>>>>

---
title: "Manuscript title here"
author: 
- name: James R Junker
  affiliation: Louisiana Universities Marine Consortium
output:
   word_document:
     reference_docx: docx_template.docx
   pdf_document:
     keep_tex: true
   html_document: default
header-includes:
- \usepackage{lineno}
- \usepackage{amsmath}
- \linenumbers
linestretch: 1
bibliography: refs.bib
link-citations: no
link-color: grey
csl: ecology.csl
---
```{r Rmarkdown setup, include = FALSE, echo=F, warning=FALSE, message=FALSE}
here::i_am("sub-projects/trawl/docs/ms/ms.RMD")

source(here::here("datascript.R"))
source(here::here("sub-project/trawl/R/Lorenz.R"))
source(here::here("sub-projects/trawl/R/Evenness.R"))

TB_trawl_data = TB_trawl_data %>%
   dplyr::filter(year %ni% c("2007","2020","2021"))

@@

Species names were checked for typos and confirmed using the *gni_parse* function from the *taxize* package [@chamberlain2020] and further standardized to consistent taxonomic resolution for entire data series (Supplemental materials). We measured multiple aspects of species richness, first to track the uncorrected accumulation of species over time we filtered species from the data set after first occurrence. We then calculated two measures of species richness, accounting for differences in abundance among trawls. The first measure was asymptotic species richness, *S~asymp~*, using the Chao1 estimator [@chao1984][@chao1987]. This metric is highly correlated with measured richness, *S* [@mcgill2011], but attempts to extrapolate the total species richness based on incomplete sampling of the community. Second, we estimated effort-controlled rarefied species richness, *S~n~*, which provides the expected number of species given a defined number of *n* individuals sampled [@gotelli2001]. For *S~n~* estimates for trawls, *n* was calculated by the minimum number of individuals within a trawl multiplied by `r n_year`. We calculated *S~asymp~* and *S~n~* using the mobr package [@mcglinn2019][@mcglinn2021a].

@@

TB_trawl_sampling = TB_trawl_data %>%
   dplyr::select(Date, year, Common_name, Abundance) %>%
   group_by(year) %>%
   dplyr::summarise(trawl_days = length(unique(Date)),
                    S = length(unique(Common_name)),
                    individuals = sum(Abundance, na.rm = TRUE))

TB_trawl_taxasite <- TB_trawl_data %>%

  dplyr::select(Date, Common_name, Abundance) %>%
  group_by(Date, Common_name) %>%
  summarise(Abundance = sum(Abundance)) %>%
  na.omit %>% group_by(Date) %>%
  # remove trawls with less than 20 individuals 
  # dplyr::filter(sum(Abundance) >=20) %>%
  group_by(Date, Common_name) %>%
  pivot_wider(names_from = Common_name, values_from = Abundance, values_fill = list(Abundance = 0)) %>%
  ungroup() %>%
  dplyr::mutate(julian_date = julian(Date, origin = as.Date("2007-01-05")),
                biweekly = ceiling(julian_date/30),
                month = month(Date),
                year = year(Date)) %>%
  dplyr::select(julian_date, Date, year, month, biweekly, everything())
